---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(fs)
library(readr)
library(gtsummary)
```

# TrackValue: Clinical Trial Transparency

This repository supports the clinical trial transparency report card project within TrackValue.

```{r trackvalue-dataset, include = FALSE}

trackvalue <-
  read_csv(here::here("data", "processed", "trackvalue.csv"))

n_ctgov <-
  trackvalue %>% 
  filter(registry == "ClinicalTrials.gov") %>% 
  nrow()

n_drks <-
  trackvalue %>% 
  filter(registry == "DRKS") %>% 
  nrow()

query_logs <- loggit::read_logs(here::here("data", "queries.log"))

get_latest_query <- function(query, logs) {
  logs %>% 
  filter(log_msg == query) %>% 
    arrange(desc(timestamp)) %>% 
    slice_head(n = 1) %>% 
    pull(timestamp) %>% 
    as.Date.character()
}
```

## Trials

The dataset is based on [IntoValue](https://doi.org/10.5281/zenodo.5141343) with updated data; see [`intovalue-data` repo](https://github.com/maia-sh/intovalue-data)) for futher details on the dataset. IntoValue inclusion criteria for completion date (2008-2018), completion status, and interventional are reapplied on trials with updated registry data.

The data was last updated on the following dates:

-   PubMed: `r get_latest_query("PubMed", query_logs)`
-   AACT (ClinicalTrials.gov): `r get_latest_query("AACT", query_logs)`
-   DRKS: `r get_latest_query("DRKS", query_logs)`
-   Unpaywall: `r get_latest_query("Unpaywall", query_logs)`
-   ShareYourPaper: `r get_latest_query("ShareYourPaper", query_logs)`

For TrackValue, we are interested in Charité-affiliated trials from recent years (i.e., more likely PIs are still at Charité), and so limit to IntoValue 2 trials with Charité listed as a lead city.

The TrackValue dataset consists of `r nrow(trackvalue)` trials, including `r n_ctgov` trials from ClinicalTrials.gov and `r n_drks` trials from DRKS.

## Report card transparency elements

TrackValue clinical trial transparency report cards may include various transparency elements. The current frontrunners are: summary results reporting, publication linkage in registry, and open access. All potential elements are included below.

### Outline

-   registration (boolean)

    -   if registration --\> registration (timely)

-   summary results (boolean)

    -   if summary results --\> summary results (timely)

-   publication (boolean)

    -   if publication --\> publication (timely)

    -   if publication --\> trn in journal publication (full-text)

    -   if publication --\> trn in journal publication (abstract)

    -   if publication --\> publication in registration

    -   if publication --\> open access (closed/open)

        -   if publication --\> if closed --\> open access (can/not be archived)

As such, some report cards would be a short as 3 items (registration timeliness, no summary results, no publication) and some as long as 10 items (registration timeliness, summary results, publication closed).

### Table

The table below provides an overview of the percentage and number of trials per registry which comply with each element.

```{r transparency-elements}

trackvalue %>%

  select(
    registry,
    is_prospective,
    has_summary_results,
    is_summary_results_1y,
    is_summary_results_2y,
    has_publication,
    is_publication_2y,
    has_iv_trn_abstract,
    has_iv_trn_ft,
    has_reg_pub_link,
    is_oa,
    is_closed_archivable
  ) %>%
  
  tbl_summary(
    by = registry,
    label = list(
      is_prospective ~ "Prospective registration",
      has_summary_results  ~ "Has registry summary results",
      is_summary_results_1y ~ "Timely summary results (12 mo)",
      is_summary_results_2y ~ "Timely summary results (24 mo)",
      has_publication ~ "Has publication",
      is_publication_2y ~ "Timely publication (24 mo)",
      has_iv_trn_abstract ~ "TRN reported in abstract",
      has_iv_trn_ft ~ "TRN reported in full-text",
      has_reg_pub_link  ~ "Publication linked in registry",
      is_oa ~ "Openly accessible",
      is_closed_archivable ~ "Closed, archivable"
    )
  ) %>%

  # Move stats legend to each line
  add_stat_label() %>%

  modify_header(label = "**TrackValue trials transparency elements**") %>%

  bold_labels() %>% 
  as_kable()

```

## EUCTR

The IntoValue, and hence TrackValue, sample includes trials any interventional study in the registry and is not limited to those regulated by German drug and medical laws. Trials regulated by those rules *should* be registered in EUCTR, rather than ClinicalTrials.gov or DRKS. As such, trials in our sample which are cross-registered in EUCTR are perhaps more likely clinical trials per German law.

```{r euctr-crossreg}

tbl_euctr <-
  trackvalue %>% 
  tbl_cross(
    row = has_crossreg_eudract,
    col = registry,
    margin = "column",
    percent = "column",
    label = list(
      has_crossreg_eudract ~ "EUCTR TRN in Registration",
      registry ~ "Registry"
    )
  )

# as_kable(tbl_euctr)
```

We found that `r inline_text(tbl_euctr, row_level = "TRUE", col_level = "Total")` trials in our sample include an EUCTR id in their registration, and are presumably cross-registered in EUCTR. This includes `r inline_text(tbl_euctr, row_level = "TRUE", col_level = "ClinicalTrials.gov")` trials from ClinicalTrials.gov and `r inline_text(tbl_euctr, row_level = "TRUE", col_level = "DRKS")` trials from DRKS.

## Open Questions

-   [ ] Timely summary results within 1 or 2 years? Or could use continuous time.
-   [ ] Should we exclude trials likely cross-registered in EUCTR?
