---
title: "TrackValue LimeSurvey Summary"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(here::here("R", "explore-limesurvey.R"))
```

As of `r Sys.Date()`, there are `r nrow(ls)` complete survey responses. Survey responses are considered complete if all required likert items were completed and includes some responses which were not submitted on the final page (n = `r ls %>% filter(!completed) %>% nrow()`).

We emailed 128 trialists. X emails bounced, so we have a response rate of X% (`r nrow(ls)`/X non-bounced emails).

## Response timeline
The survey was launched on `r date_launch`. `r n_launch` responses were before reminder 1 from cvk on `r date_reminder_1`. `r n_reminder_1` responses were after reminder 1.

## Materials
`r n_no_materials` respondents reported not reviewing the materials prior to starting the survey. The survey prompted these respondents to review the materials and return to survey.

## Corrections
`r n_complete_corrections` complete responses included corrections. Corrections are separated from responses and will be analysed separately. As such, we include all corrections, including from incomplete survey responses (i.e., likert incomplete) and therefore have corrections from `r n_distinct(ls_corrections$id)` respondents (complete and partial); it looks like a respondent got stuck on the corrections because they didn't put a trn, so this is good to note for future survey design. Below are the corrections, which we should analyze/address manually separately. TODO: We should decide how/where to do this.

```{r corrections}
ls_corrections %>% 
  select(trn, correction) %>% 
  knitr::kable()
```

## Changes and comments
Some respondents suggested changes and/or provided comments, which we should analyze/address manually separately. TODO: We should decide how/where to do this.

```{r changes-comments}
changes_comments %>% 
  mutate(text = paste0("- ", type, ": ", text)) %>% 
  select(text) %>% 
  knitr::kable()
  # cat(sep = "\n")
```

## Roles
Most respondents were study leaders and/or doctors.

```{r roles}
plot_roles
```

## Likert
Self-reported usefulness of the report card and infosheet varied widely, with slightly positive average.

```{r likert}
# likert_display
likert_summary %>% 
  knitr::kable()
```
